other functionalities

### 2024-03-22 inst/gitbook/05_other-functionalities.Rmd
Update 05_other-functionalities.Rmd

```{r}
## Treating missing data as all data values
default_behaviour <- list(missing      <- function(x,y) y,
## Treating inapplicable data as all data values (like missing)    
                          inapplicable <- function(x, y) y,
## Treating polymorphisms as all values present:
                          polymorphism <- function(x,y) strsplit(x, split = "\\&")[[1]],
## Treating uncertainties as all values present (like polymorphisms):
                          uncertanity  <- function(x,y) strsplit(x, split = "\\&")[[1]])
```

>>>>

```{r}
## Treating missing data as all data values
default_behaviour <- list(missing      <- function(x,y) y,
## Treating inapplicable data as all data values (like missing)    
                          inapplicable <- function(x, y) y,
## Treating polymorphisms as all values present:
                          polymorphism <- function(x,y) strsplit(x, split = "\\&")[[1]],
## Treating uncertainties as all values present (like polymorphisms):
                          uncertanity  <- function(x,y) strsplit(x, split = "\\/")[[1]])
```
